---
title: "House Pricing Analysis"
author: "Prabha"
date: "4/22/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Exploratory Analysis
### Lets combine train and test datasets for data cleaning activity
```{r }
library(dplyr)
load('/Users/prabha/GitHub/Kaggle/House Prices/.RData')
colnames(train)[44]="1stFlrSF"
colnames(train)[45]="2ndFlrSF"
colnames(train)[70]="3SsnPorch"
colnames(test[,-1])==colnames(train[,-c(1,81)])
```

Now train and test column names are same.Lets combine by removing id column and SalesPrice (which is dependent varaible we are trying to predict)
```{r}
combined=rbind(train[,-c(1,81)],test[,-1])
nrow(combined)
```

Finding how many NAs, 

```{r}
sort(sapply(combined,function(x) sum(is.na(x))),decreasing=T)
```

First lets tackle PoolQC, Only table observations has values other are NA. Let's see if we have any NA for poolArea >0
```{r}
filter(combined,PoolArea>0 & is.na(PoolQC))[,c('PoolArea','PoolQC')]
with(combined,which(PoolArea>0 & is.na(PoolQC)))
```

see the Average PoolArea for different PoolQC, Fill the NA where you have PoolArea > 0 using the below mean
```{r}
combined %>% 
group_by(PoolQC) %>% 
summarise(mean_PoolArea=mean(PoolArea))
combined[c(2421,2504,2600),c('PoolArea','PoolQC')]
combined[2421,'PoolQC']="Ex"
combined[2504,'PoolQC']="Ex"
combined[2600,'PoolQC']="Fa"
```
Other NA value replace with "None"

```{r}
combined$PoolQC=as.character(combined$PoolQC)
combined$PoolQC[is.na(combined$PoolQC)]="None"
```


finding unique values

```{r}
sort(sapply(combined,function(x) length(unique(x))))
```

